\textbf{Traffic Analysis} \\ {\Large\itshape A write-up}

### 2019-03-12 paper.tex
post-supper

\documentclass[11pt]{diazessay} % Font size (can be 10pt, 11pt or 12pt)
\usepackage{float}
\usepackage{sectsty}
\usepackage[numbers]{natbib}
\sectionfont{\centering}
\usepackage{listings}
\usepackage{color}

@@

\lstset{ 
%         language=Matlab,                                % choose the language of the code
%       basicstyle=10pt,                                % the size of the fonts that are used for the code
%         numbers=left,                                   % where to put the line-numbers
%         numberstyle=\footnotesize,                      % the size of the fonts that are used for the line-numbers
%         stepnumber=1,                                           % the step between two line-numbers. If it's 1 each line will be numbered
%         numbersep=5pt,                                  % how far the line-numbers are from the code
%       backgroundcolor=\color{white},          % choose the background color. You must add \usepackage{color}
%         showspaces=false,                               % show spaces adding particular underscores
%         showstringspaces=false,                         % underline spaces within strings
%         showtabs=false,                                         % show tabs within strings adding particular underscores
%       frame=single,                                           % adds a frame around the code
%       tabsize=2,                                              % sets default tabsize to 2 spaces
%       captionpos=b,                                           % sets the caption-position to bottom
         breaklines=true,                                        % sets automatic line breaking
%         breakatwhitespace=false,                        % sets if automatic breaks should only happen at whitespace
%         escapeinside={\%*}{*)}                          % if you want to add a comment within your code
}

\lstset{frame=tb,
  language=php,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

@@

\section{Introduction}
This analysis examines events that took place on a South African network on the 2017-03-20 and 2017-03-22. We will make the argument, based purely on captured network traffic, that a host was compromised with a ransomware variant known as Maktub. Ransomware is the term used to describe malicious software that either encrypts data (thus denying access), or threatens to leak data. The attacker will offer to stop the attack if payment is received thus the name ransomware. Maktub is of the encryption variant and is usually delivered via an email attachment, which appears legitimate but performs its malicious activity in the background.

@@

\section{Traffic Overview}

@@

The three graphs depict packets per 10 seconds for a full network capture over the period, followed by traffic generated on the 20th and 22nd. The traffic was divided in this way to logically separate the behavior associated with each time sequence. The story of the infected host is encapsulated on the first day, whereas the second day exhibits indirect behavior of the infected host as the machine has been taken offline.

A point to make about attacks of this kind, is that they can easily slip between the cracks since benign traffic is by far the most dominant communication on the network. Most of the traffic generated involves the target host receiving legitimate windows updates from trusted IP addresses. In monitoring the DNS traffic closely we found some interesting queries for known malicious sites. We set out to uncover when the infection shows and how communication with the C2 (command and control server) was carried out.

@@

\section{Traffic for initial compromise}

On the 2017-03-20 our host (10.0.0.5) seems to be engaged in routine Windows updates from IPs associated with Microsoft and Akamai (A legitimate CDN, content distribution network). The first signs of anomalous activity commence. A mail with an attachment, potentially a msword document is fetched after a "503 Backend fetch failed". The destination IP is associated with a onion domain (Host: 45jngpxc4cgsxqxc.onion.link). The .onion domain refers to TOR hidden services which require the TOR browser to interpret the protocol and connect to the site. TOR is a privacy oriented protocol which aims to obscure the origin of the sender, by encapsulating a packet in three layers of encryption before routing the packet through three intermediaries nodes on the way to the server. The protocol serves a valuable role to actors of differing motivation. The protocol is not only used by activists and those most vulnerable but also those who exploit it for profit. The ".link" allows for for convenience at the expense of \cite{onionlink}. This allowed the target system to visit a TOR hidden service hosted by our attackers. The onion link confirms our suspicions as it is associated with a malware analysis of an malicious windows executable inserted inside a benign looking update policy word document \cite{hybrid}.

\begin{lstlisting}
2017-03-20 15:20:08.517517 IP (tos 0x0, ttl 128, id 4560, offset 0, flags [DF], proto TCP (6), length 551)
    10.0.0.5.52848 > 103.198.0.2.80: Flags [P.], cksum 0x4696 (correct), seq 1:512, ack 1, win 4236, length 511: HTTP, length: 511
        GET / HTTP/1.1
        Accept: image/jpeg, application/x-ms-application, image/gif, application/xaml+xml, image/pjpeg, application/x-ms-xbap, application/vnd.ms-excel, application/vnd.ms-powerpoint, application/msword, */*
        Accept-Language: en-US
        User-Agent: Mozilla/4.0 (compatible; MSIE 8.0; Windows NT 6.1; Trident/4.0; SLCC2; .NET CLR 2.0.50727; .NET CLR 3.5.30729; .NET CLR 3.0.30729; Media Center PC 6.0; InfoPath.2)
        Accept-Encoding: gzip, deflate
        Host: 45jngpxc4cgsxqxc.onion.link
        Connection: Keep-Alive

E..'..@...u4
...g....p.P*R>....*P...F...GET / HTTP/1.1
Accept: image/jpeg, application/x-ms-application, image/gif, application/xaml+xml, image/pjpeg, application/x-ms-xbap, application/vnd.ms-excel, application/vnd.ms-powerpoint, application/msword, */*
Accept-Language: en-US
User-Agent: Mozilla/4.0 (compatible; MSIE 8.0; Windows NT 6.1; Trident/4.0; SLCC2; .NET CLR 2.0.50727; .NET CLR 3.5.30729; .NET CLR 3.0.30729; Media Center PC 6.0; InfoPath.2)
Accept-Encoding: gzip, deflate
Host: 45jngpxc4cgsxqxc.onion.link
Connection: Keep-Alive

2017-03-20 15:20:08.790039 IP (tos 0x18, ttl 52, id 30272, offset 0, flags [DF], proto TCP (6), length 524)
    103.198.0.2.80 > 10.0.0.5.52848: Flags [P.], cksum 0x6305 (correct), seq 1:485, ack 512, win 123, length 484: HTTP, length: 484
        HTTP/1.1 503 Backend fetch failed
        Date: Mon, 20 Mar 2017 08:21:16 GMT
        Content-Type: text/html; charset=utf-8
        Retry-After: 5
        Age: 0
        X-Cache: MISS
        Content-Length: 286
        Connection: keep-alive

        <!DOCTYPE html>
        <html>
          <head>
            <title>503 Backend fetch failed</title>
          </head>
          <body>
            <h1>Error 503 Backend fetch failed</h1>
            <p>Backend fetch failed</p>
            <h3>Guru Meditation:</h3>
            <p>XID: 288687254</p>
            <hr>
            <p>Varnish cache server</p>
          </body>
        </html>
    103.198.0.2.80 > 10.0.0.5.52849: Flags [P.], cksum 0x7d3d (correct), seq 1:1133, ack 311, win 123, length 1132: HTTP, length: 1132
        HTTP/1.1 500 Internal Server Error
        Content-Length: 856
        Content-Encoding: gzip
        X-Check-Tor: false
        Content-Security-Policy: upgrade-insecure-requests
        X-Onion-Url: 45jngpxc4cgsxqxc.onion
        Date: Mon, 20 Mar 2017 08:21:20 GMT
        Age: 0
        X-Cache: MISS
        Connection: keep-alive

E.....@.4..zg...
....P.q!'(.k.k}P..{}=..HTTP/1.1 500 Internal Server Error
Content-Length: 856
Content-Encoding: gzip
X-Check-Tor: false
Content-Security-Policy: upgrade-insecure-requests
X-Onion-Url: 45jngpxc4cgsxqxc.onion
Date: Mon, 20 Mar 2017 08:21:20 GMT
Age: 0
X-Cache: MISS
Connection: keep-alive

...........U[o.6.~v~....{.........@...k2.1..c..E2$....!\%........|.....Y.[Y\..5......^Bq..V.B=..Rw."J{Rj....k2..Q.....v..}..`............9...,<.(.n.........{..s'.9...?........6.....E;...`O..-........(.4..9el.....p.\.2.9-...n.... s..A.k.|.8.\i....2....3.7|..Z.....-u....+.6.....N?...M.
.n.-2..+.2..*dm......[RJ.\N.B
.Yn.X...D..h......E...-S.jJ..............g...Y.....pb......+....*..k..../I....Q7x.....r\%....NT...l:=.}2..r..[p....5...........?....W..Z....B2.....H..(._JQ>.t...O..s..7..]P"*,.~.....+x{ .~..X..E.k.......S3.........7(LK.wB.D..\..0G.$.2..B.......,...'y.......,H...   .{.|.a....)Tz.^.,.;N<.F[..iDYv...U<hK....Og....3f.oFi....>.
.1{.$.W....CI..bmqJ......2c...S...1...O.._xk......J.......;'.E_qs...../.....S.!...}.}.N!I....c..V..c..o\%.2.R.....D...l...0..m....?.....?}K.X.........ry?`~...........xl...-.....c.:yN   ~......n.36z..n.#|..qn..M..w..t.......

    10.0.0.5.137 > 103.198.0.2.137: [udp sum ok]
>>> NBT UDP PACKET(137): QUERY; REQUEST; BROADCAST
TrnID=0xF66C
OpCode=0
NmFlags=0x1
Rcode=0
QueryCount=1
AnswerCount=0
AuthorityCount=0
AddressRecCount=0
QuestionRecords:
Name=*               NameType=0x00 (Workstation)
QuestionType=0x21
QuestionClass=0x1
\end{lstlisting}
\begin{lstlisting}
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61226         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.198.103.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61226         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.198.103.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61226         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61226         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.198.103.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52849         -> 103.198.0.2:80         [http] Request { method: "GET", uri: "/favicon.ico", version: "1.1", host: Some("45jngpxc4cgsxqxc.onion.link"), agent
: Some("Mozilla/4.0 (compatible; MSIE 8.0; Windows NT 6.1; Trident/4.0; SLCC2; .NET CLR 2.0.50727; .NET CLR 3.5.30729; .NET CLR 3.0.30729; Media Center PC 6.0; InfoPath.2)"), referer: None, auth: None, cookies: N
one }
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61226         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61226         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61226         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.198.103.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61226         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:51704         -> 10.0.0.2:53            [dns] req, (A, "45jngpxc4cgsxqxc.torstorm.org")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:51704         [dns] resp, ("45jngpxc4cgsxqxc.torstorm.org", A(94.242.58.199))
                                                                                                           ("45jngpxc4cgsxqxc.torstorm.org", A(192.64.119.254))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49695         -> 10.0.0.2:53            [dns] req, (AAAA, "45jngpxc4cgsxqxc.torstorm.org")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49695         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:57862         -> 10.0.0.2:53            [dns] req, (PTR, "199.58.242.94.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:57862         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52851         -> 192.64.119.254:80      [http] Request { method: "GET", uri: "/", version: "1.1", host: Some("45jngpxc4cgsxqxc.torstorm.org"), agent: Some("M
ozilla/4.0 (compatible; MSIE 8.0; Windows NT 6.1; Trident/4.0; SLCC2; .NET CLR 2.0.50727; .NET CLR 3.5.30729; .NET CLR 3.0.30729; Media Center PC 6.0; InfoPath.2)"), referer: None, auth: None, cookies: None }
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [tcp] 192.64.119.254:80      -> 10.0.0.5:52851         [text] "HTTP/1.1 302 Found\r\nServer: nginx\r\nDate: Mon, 20 Mar 2017 13:20:33 GMT\r\nContent-Type: text/html; charse
t=utf-8\r\nContent-Length: 45\r\nConnection: keep-alive\r\nLocation: https://cryptostorm.is\r\nX-Served-By: Namecheap URL Forward\r\n\r\n<a href=\"https://cryptostorm.is\">Found</a>.\n\n"
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:60307         -> 10.0.0.2:53            [dns] req, (PTR, "254.119.64.192.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:50923         -> 10.0.0.2:53            [dns] req, (A, "cryptostorm.is")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:50923         [dns] resp, ("cryptostorm.is", A(46.165.240.186))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52680         -> 10.0.0.2:53            [dns] req, (AAAA, "cryptostorm.is")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52680         -> 10.0.0.2:53            [dns] req, (AAAA, "cryptostorm.is")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:60307         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:60307         -> 10.0.0.2:53            [dns] req, (PTR, "254.119.64.192.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:60307         -> 10.0.0.2:53            [dns] req, (PTR, "254.119.64.192.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52680         -> 10.0.0.2:53            [dns] req, (AAAA, "cryptostorm.is")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52680         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52680         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52680         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:60307         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:60307         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:60307         -> 10.0.0.2:53            [dns] req, (PTR, "254.119.64.192.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52852         -> 46.165.240.186:443     [tls] ClientHello (hostname: "cryptostorm.is")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:60307         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61872         -> 10.0.0.2:53            [dns] req, (PTR, "186.240.165.46.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61872         [dns] resp, ("186.240.165.46.in-addr.arpa", PTR("cryptostorm.is"))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:59404         -> 10.0.0.2:53            [dns] req, (A, "ocsp.comodoca.com")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:59404         [dns] resp, ("ocsp.comodoca.com", A(178.255.83.1))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:64237         -> 10.0.0.2:53            [dns] req, (AAAA, "ocsp.comodoca.com")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:64237         [dns] resp, ("ocsp.comodoca.com", AAAA(2a02:1788:2fd::b2ff:5301))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:64237         -> 10.0.0.2:53            [dns] req, (AAAA, "ocsp.comodoca.com")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:64237         [dns] resp, ("ocsp.comodoca.com", AAAA(2a02:1788:2fd::b2ff:5301))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52853         -> 178.255.83.1:80        [http] Request { method: "GET", uri: "/MFEwTzBNMEswSTAJBgUrDgMCGgUABBReAhtobFzTvhaRmVeJ38QUchY9AwQUu69\%2BAj36pvE8hI6t
7jiY7NkyMtQCECsuburZdTZsFIpu26N8jAc\%3D", version: "1.1", host: Some("ocsp.comodoca.com"), agent: Some("Microsoft-CryptoAPI/6.1"), referer: None, auth: None, cookies: None }
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:54122         -> 10.0.0.2:53            [dns] req, (PTR, "1.83.255.178.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:54122         [dns] resp, ("1.83.255.178.in-addr.arpa", PTR("ocsp.comodoca.com"))
\end{lstlisting}
\begin{lstlisting}
Put your code here.
\end{lstlisting}
\begin{lstlisting}
Put your code here.
\end{lstlisting}

@@

\begin{lstlisting}
("45jngpxc4cgsxqxc.torstorm.org", A(94.242.58.199))
\end{lstlisting}

@@

\begin{lstlisting}
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "255.0.0.10.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.0.10.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "252.0.0.224.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "5.0.0.10.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "252.0.0.224.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.0.10.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "5.7.a.9.c.3.8.2.0.0.c.0.a.f.1.8.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:53658         -> 10.0.0.2:53            [dns] req, (PTR, "255.0.0.10.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:53658         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:59669         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:51331         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.0.10.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:59669         -> 10.0.0.2:53            [dns] req, (PTR, "1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:55984         -> 10.0.0.2:53            [dns] req, (PTR, "3.0.0.0.1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:58967         -> 10.0.0.2:53            [dns] req, (PTR, "252.0.0.224.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:55984         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:51331         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:58967         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:63635         -> 10.0.0.2:53            [dns] req, (PTR, "255.255.255.255.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:51846         -> 10.0.0.2:53            [dns] req, (PTR, "250.255.255.239.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:63635         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:51846         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49692         -> 10.0.0.2:53            [dns] req, (PTR, "1.0.0.0.0.0.f.f.1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49692         -> 10.0.0.2:53            [dns] req, (PTR, "1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49692         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49692         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49693         -> 10.0.0.2:53            [dns] req, (PTR, "250.255.255.239.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49693         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "4.0.0.10.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "5.1.d.4.7.0.1.6.5.6.b.d.d.3.0.f.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "c.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "6.1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "22.0.0.224.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, ("22.0.0.224.in-addr.arpa", PTR("igmp.mcast.net"))
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49695         -> 10.0.0.2:53            [dns] req, (PTR, "255.255.255.255.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49695         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49696         -> 10.0.0.2:53            [dns] req, (PTR, "3.f.e.9.4.5.8.2.8.6.b.b.6.2.c.7.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")

>>>>

\documentclass[11pt]{diazessay} % Font size (can be 10pt, 11pt or 12pt)
\usepackage{float}
\usepackage{sectsty}
\usepackage{appendix}
\usepackage[numbers]{natbib}
\sectionfont{\centering}
\usepackage{listings}
\usepackage{color}

@@

%\lstset{ 
%         language=Matlab,                                % choose the language of the code
%       basicstyle=10pt,                                % the size of the fonts that are used for the code
%         numbers=left,                                   % where to put the line-numbers
%         numberstyle=\footnotesize,                      % the size of the fonts that are used for the line-numbers
%         stepnumber=1,                                           % the step between two line-numbers. If it's 1 each line will be numbered
%         numbersep=5pt,                                  % how far the line-numbers are from the code
%       backgroundcolor=\color{white},          % choose the background color. You must add \usepackage{color}
%         showspaces=false,                               % show spaces adding particular underscores
%         showstringspaces=false,                         % underline spaces within strings
%         showtabs=false,                                         % show tabs within strings adding particular underscores
%       frame=single,                                           % adds a frame around the code
%       tabsize=2,                                              % sets default tabsize to 2 spaces
%       captionpos=b,                                           % sets the caption-position to bottom
%         breakatwhitespace=false,                        % sets if automatic breaks should only happen at whitespace
%         escapeinside={\%*}{*)}                          % if you want to add a comment within your code
%}

\lstset{frame=tb,
  breaklines=true,                                        % sets automatic line breaking
  language=php,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

@@

\section*{Introduction}
This analysis examines events that took place on a South African network on the 2017-03-20 and 2017-03-22. We will make the argument, based purely on captured network traffic, that a host was compromised with a ransomware variant known as Maktub. Ransomware is the term used to describe malicious software that either encrypts data (thus denying access), or threatens to leak data. The attacker will offer to stop the attack if payment is received thus the name ransomware. Maktub is of the encryption variant and is usually delivered via an email attachment, which appears legitimate but performs its malicious activity in the background.

@@

\section*{Traffic Overview}

@@

% STANDTHIS
This analysis examines events that took place on a South African network on the 2017-03-20 and 2017-03-22. We will make the argument, based purely on captured network traffic and inferences gleaned from prior malware analysis, that a host was compromised with a ransomware variant known as Maktub.

% DAN 
The three graphs depict packets per 10 seconds for a the compete pcap sample, followed by traffic generated on the 20th and 22nd. The traffic was divided in this way to logically separate the behavior associated with each time sequence. The story of the infected host is encapsulated on the first day, whereas the second day exhibits indirect behavior of the infected host as the machine has been taken offline.

A point to make about attacks of this kind, is that they can easily slip between the cracks since benign traffic is by far the most dominant communication on the network. Most of the traffic generated involves the target host receiving legitimate windows updates from trusted IP addresses.

In monitoring the DNS traffic closely we found some interesting queries for known malicious sites. We set out to uncover the initial execution point of the malicious code and how communication with the C2 (command and control server) was carried out.

@@

\section*{Traffic for initial compromise on the 20th}

% DAN
On the 2017-03-20 our host (10.0.0.5) seems to be engaged in routine Windows updates from IPs associated with Microsoft and Akamai (A legitimate CDN, content distribution network). The first signs of anomalous activity commence from what appears to be a span mail. A mail with an attachment, potentially a Microsoft Word document, is fetched after a "503 Backend fetch failed" response. The following request is made to a destination IP associated with an onion domain (Host: 45jngpxc4cgsxqxc.onion.link). The .onion domain refers to TOR hidden services which require the TOR browser to interpret the protocol and connect to the site. TOR is a privacy oriented protocol which aims to obscure the origin of the sender, by encapsulating a packet in three layers of encryption before routing the packet through three intermediaries nodes on the way to the server. The protocol serves a valuable role to actors of differing motivation. The protocol is not only used by activists and those circumventing censorship but also those who exploit it for profit. The ".link" allows for for convenience at the expense of privacy, as your service provider can see your what content you are requesting \cite{onionlink}. The host also visited  torstorm.org domain, which offers a similar service. This allowed the target system to visit a TOR hidden services hosted by our attackers. The onion link confirms our suspicions as it is associated with a malware analysis of a malicious windows executable inserted inside a benign looking update policy word document \cite{hybrid}. Please refer to appendix A for the TCP conversation of the payload delivery.

@@

\begin{lstlisting}[language=html]
("45jngpxc4cgsxqxc.torstorm.org", A(94.242.58.199))
\end{lstlisting}

@@

%Tor2web listing
